\vspace{-1in} \usefont{OT1}{bch}{b}{n} \normalfont \normalsize \textsc{CSEC-472 Authentication Paper} \\ [14pt] \huge A Security Analysis of the Lenel BlueDiamond \\

### 2020-05-07 paper/paper/paper.tex
fixing minor issues

\section{Background \& Significance}
Throughout history, people have tried to gain access restricted areas. \cite{lockpickinghistory}  Locks were created in order to restrict access, but locksmiths were often skeptical of their inventions, and if they could be bypassed.  The first documented case of lock picking was a challenge released by Joseph Bramah, an Enlish locksmith.  Bramah had just developed his so called safety lock.  His lock had safety features that he believed to be completely secure.  Obviously, nothing is ever completely secure, but Bramah put it to the test by announcing a contest.  Anyone who could break into his new creation would net a cool sum of 20,000 pounds.

While the Bramah challenge was still in place, another locksmith caught wind of Bramah's idea.  Jeremiah Chubb built a lock that would alert an owner if any sort of picking had been detected.  He too, announced a challnge.  An American Locksmith named A.C. Hobbs took up the challenge, and had it open within an hour of touching the lock.  However, that wasn't the only challenge he accepted.  Chubb took a trip over to Hobbs' locksmithing shop, and 70 years later, picked the Bramah security lock.

New technology leads to new innovation.  Almost overnight, businesses and organizations started using electronic locking systems for their ease of use and simplicity in granting or denying access.  Granting access to a building is as simple as a few button clicks.  For most organizations, it is much easier to spend the extra money for a digital system with computer-controlled access control than to re-key a lock every single time an employee leaves the organization.

@@

Other protocols for IoT communications are not free of issues either. Chung shows the Wiegand is still vulnerable to a decade old attack in modern devices. An attacker can intercept and then duplicate the signals sent by a Wiegand device to the control server. This attack can capture and repeat and authorized card without needing to physically duplicate the card \cite{chung2017wiegand}. Hakamaki and Palomaki discuss a number of existing RFID attacks that still exist in modern RFID readers \cite{rfid15}.

@@

\subsection{Data Measurement \& Analysis}
As this is primarily a penetration test of the Lenel BlueDiamond, there are four quantitative metrics of note: number of vulnerabilities, severity, likelihood, and risk. A vulnerability is counted if it could be exploited for an unintened effect. The severity, likelihood, and risk can be properly measured by the Common Vulnerability Scoring System, or CVSS 3.x. This would allow for a more uniform scoring standard inline with what the industry uses. Vulnerabilties will be discovered by a number of tools, including devices like the Ubertooth, manual tool usage, and fuzzing. Vulnerabilities found would be sorted based on protocol and CVSS score. This would allow for a clearer picture into the vulnerabilities for each protocol and the risk associated with using them. Once a vulnerability is discovered, an exploit would be attempted to practicality. Practicality is to measure the ease of attack. It is directly proportional to the likelihood, and provides further insight into likelihood than a CVSS score can.

\subsection{Procedures}
The testing performed against the readers would be broken into three primary categories: Bluetooth, RFID, and Wiegand.  These categories will follow logical attack chains to test a variety of vulnerabilites.

@@

\subsection{Timeline}
The timeline for this project assumes a eight week period for testing.  This eight week period will be broken up into five separate stages for setup, testing, and wrapup.  Eight weeks should be more than adequate to perform the necessary testing and provide a complete report.  The first period is one week long and dedicated to setup.  During this time a test lab would be built with the necessary equipment to test RFID, Bluetooth, and Wiegand.  The second period is two weeks in length and dedicated to testing RFID.  The third period is also two weeks in length, this is dedicated to testing for Bluetooth weaknesses.  The fourth period is the final two week period, this time dedicated to testing for Wiegand vulnerabilities.  The fifth and final period is one week in length, unlike the others this period is not for testing.  The last period is dedicated to writing the report to submit to Carrier for their review.

\section{Preliminary Suppositions \& Implications}
This reasearch will expand and refine on the current work available on Lenel readers and readers in general. While we could find several research papers on BLE lock examination \cite{matthewrs2017surveydoorlock}\cite{ho2016smart}\cite{ye2017security}\cite{8887393}, we found no research on readers that offer multiple protocols for communication. We have a opportunity to add insight on examining mutli-protocol readers and how to approached examining and attacking them. In addition, we could find very little on attack chains for RFID or Wiegand based attacks \cite{chung2017wiegand}. Our work will allow for the creating of a preliminary attack chain for these protocols.

>>>>

\section{Background \& Significance}
Throughout history, people have tried to gain access to restricted areas. \cite{lockpickinghistory}  Locks were created in order to restrict access, but locksmiths were often skeptical of their inventions, and if they could be bypassed.  The first documented case of lock picking was a challenge released by Joseph Bramah, an English locksmith.  Bramah had just developed his so-called safety lock.  His lock had safety features that he believed to be completely secure.  Obviously, nothing is ever completely secure, but Bramah put it to the test by announcing a contest.  Anyone who could break into his new creation would net a cool sum of 20,000 pounds.

While the Bramah challenge was still in place, another locksmith caught wind of Bramah's idea.  Jeremiah Chubb built a lock that would alert an owner if any sort of picking had been detected.  He too, announced a challenge.  An American Locksmith named A.C. Hobbs took up the challenge, and had it open within an hour of touching the lock.  However, that wasn't the only challenge he accepted.  Chubb took a trip over to Hobbs' locksmithing shop, and 70 years later, picked the Bramah security lock.

New technology leads to new innovation.  Almost overnight, businesses and organizations started using electronic locking systems for their ease of use and simplicity in granting or denying access.  Granting access to a building is as simple as a few button clicks.  For most organizations, it is much easier to spend the extra money for a digital system with computer-controlled access control than to rekey a lock every single time an employee leaves the organization.

@@

Other protocols for IoT communications are not free of issues either. Chung shows the Wiegand is still vulnerable to a decade old attack in modern devices. An attacker can intercept and then duplicate the signals sent by a Wiegand device to the control server. This attack can capture and repeat an authorized card without needing to physically duplicate the card \cite{chung2017wiegand}. Hakamaki and Palomaki discuss a number of existing RFID attacks that still exist in modern RFID readers \cite{rfid15}.

@@

\subsection{Data Measurement \& Analysis}
As this is primarily a penetration test of the Lenel BlueDiamond, there are four quantitative metrics of note: number of vulnerabilities, severity, likelihood, and risk. A vulnerability is counted if it could be exploited for an unintended effect. The severity, likelihood, and risk can be properly measured by the Common Vulnerability Scoring System, or CVSS 3.x. This would allow for a more uniform scoring standard inline with what the industry uses. Vulnerabilities will be discovered by a number of tools, including devices like the Ubertooth, manual tool usage, and fuzzing. Vulnerabilities found would be sorted based on protocol and CVSS score. This would allow for a clearer picture into the vulnerabilities for each protocol and the risk associated with using them. Once a vulnerability is discovered, an exploit would be attempted to practicality. Practicality is to measure the ease of attack. It is directly proportional to the likelihood, and provides further insight into likelihood than a CVSS score can.

\subsection{Procedures}
The testing performed against the readers would be broken into three primary categories: Bluetooth, RFID, and Wiegand.  These categories will follow logical attack chains to test a variety of vulnerabilities.

@@

\subsection{Timeline}
The timeline for this project assumes an eight week period for testing.  This eight week period will be broken up into five separate stages for setup, testing, and wrap up.  Eight weeks should be more than adequate to perform the necessary testing and provide a complete report.  The first period is one week long and dedicated to set up.  During this time a test lab would be built with the necessary equipment to test RFID, Bluetooth, and Wiegand.  The second period is two weeks in length and dedicated to testing RFID.  The third period is also two weeks in length, this is dedicated to testing for Bluetooth weaknesses.  The fourth period is the final two week period, this time dedicated to testing for Wiegand vulnerabilities.  The fifth and final period is one week in length, unlike the others this period is not for testing.  The last period is dedicated to writing the report to submit to Carrier for their review.

\section{Preliminary Suppositions \& Implications}
This research will expand and refine on the current work available on Lenel readers and readers in general. While we could find several research papers on BLE lock examination \cite{matthewrs2017surveydoorlock}\cite{ho2016smart}\cite{ye2017security}\cite{8887393}, we found no research on readers that offer multiple protocols for communication. We have a opportunity to add insight on examining multi-protocol readers and how to approached examining and attacking them. In addition, we could find very little on attack chains for RFID or Wiegand based attacks \cite{chung2017wiegand}. Our work will allow for the creating of a preliminary attack chain for these protocols.
